full title

### 2020-11-02 paper/pldi21/abstract.tex
Revised abstract

\begin{abstract}
Static analyses based on abstract interpretation can be integrated into developer workflow and help developers to find bugs.
However, the dynamic features of JavaScript degrade the scalability and precision of the pure static analyses.
Combining static and dynamic analyses is one of the breakthroughs in JavaScript bug detection.
Existing combined analyses have static boundaries that distinguish which analysis used for which part of a program.
Such boundaries are intuitive but limit chances to optimize transitions between two analyses.
We formally present the dynamic shortcut, a more flexible compound of static and dynamic analyses.
We implement a proof of concept bug detector by extending the existing static analyzer supporting a subset of ECMAScript 5.1.
Our experimental results show that the combined analysis indeed speeds up and produces more precise results.
\end{abstract}

>>>>

\begin{abstract}
  JavaScript becomes one of the most widely used programming languages for web
  development, server-side programming, and embedded systems.  However, its
  dynamic language features degrade the scalability and precision of the static
  analysis.  Moreover, the variety of built-in functions and host environments
  requires excessive manual modeling of their behaviors for the static analysis
  of real-world JavaScript applications.  To alleviate this problem, several
  researchers utilize the dynamic analysis to take its advantage during
  JavaScript static analysis.  However, most of them sacrifice the soundness
  and focus on only reducing the effort of manual modeling.

  In this paper, we propose a novel \textit{dynamic shortcut} technique to
  leverage high performance of dynamic analysis for static analysis in a sound
  way.  It could significantly accelerate the JavaScript static analysis by
  using the highly-optimized commercial JavaScript engines for the concretely
  executable program parts.  Moreover, it might improve the precision and lessen
  the modeling effort by performing dynamic analysis for opaque codes.  To
  maximize the usage of dynamic analysis, we propose \textit{sealed symbolic
  execution}, which is an augmented concrete execution that represents abstract
  values as sealed symbolic values.  We formally define the static analysis with
  dynamic shortcut using sealed symbolic execution.  We actualize our method via
  $\tool$, which is an extension of the existing JavaScript static analyzer
  $\safe$ with dynamic shortcut.  For evaluation of $\tool$, we analyzed
  abstracted versions of \inred{77} official tests of \inred{Lodash 4} library.
  Our tool is \inred{X.X}x faster than the original static analysis on average.
  Moreover, it improves \inred{XX.XX}\% of analysis precision by using dynamic
  analysis instead of static analysis for \inred{XX.X} opaque functions on
  average.
\end{abstract}
